Presentasjon OPX Fiffig tittel

### 2022-07-29 Presentasjon/presentasjon.Rmd
Lagt til kommentar om staving/syntaks.

## <br> Introduction | OPX and their goal
- A startup developing solutions for socially responsible investment strategies
- The goal is to increase cash flow to charitable purposes 
- Donor's trust in NGOs' financial performance and their ability to deliver results is crucial for their choice of beneficients

>>>>

## <br> Introduction | OPX and their goal
- A startup developing solutions for socially responsible investment strategies
- The goal is to increase cash flow to charitable purposes 
- Donor's trust in NGOs' financial performance and their ability to deliver results is crucial for their choice of beneficients <!-- # Donors' (or: A donor's); beneficiaries --TSO -->
